Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-05 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

The sizing check stage can ensure that the system meets the standard project steps related to the critical period method (worst month) for solar energy system sizing~\cite{Pinho} and adopting an MPPT (Maximum Power Point Tracking) charge controller, which is the most common in use. Firstly, we need to correct the daily energy consumption estimated for the load ($E_{consumption}$), which is carried out by Eq.~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho}.

\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{\eta_{b} \times \eta_{c} \times \eta_{i} }
\end{equation}

We must estimate the total power that will be demanded from the PV panels, as defined by Eq. ~\eqref{eq:Pminpanel}. Where $Insolation$, also called solar irradiation or solar exposure, is expressed in terms of $kWh/m^{2}$ per day and depends on the site where the PV system will be deployed. \textcolor{blue}{An empirical factor of $20$\% for losses is considered~\cite{Pinho}}, because $1.25 = 1 \mathbin{/} (1 - 0.2)$.

\begin{equation}
\label{eq:Pminpanel}
P_{min,panels} = \dfrac{1.25 \times E_{corrected}}{Insolation}
\end{equation}

On the one hand, the sizing must meet this requirement of minimum power supplied from the PV panels $P_{min,panels}$. On the other hand, the arrangement, if in series or parallel connections, it will depend on the charge controller specification of current $I_{c}$ and voltage $V_{c}$, as described by Eqs.~\eqref{eq:Icmin} and \eqref{eq:Vcmin}.

\begin{subequations}
 \begin{tabularx}{\textwidth}{Xp{1cm}X}
\begin{equation}
\label{eq:Icmin}
I_{c} \geq I_{total,PVpanels}
\end{equation}
 & &
\begin{equation}
\label{eq:Vcmin}
V_{c} \geq V_{total,PVpanels}
\end{equation}
\end{tabularx}
\end{subequations}

Concerning the batteries, the energy $E_{b}$ to be demanded by the PV system, in order to meet the load requirements, is defined by Eq.~\eqref{eq:Ebat}.

\begin{equation}
\label{eq:Ebat}
E_{b} = \dfrac{Autonomy \times E_{corrected}}{DOD}
\end{equation}

\noindent Where $Autonomy$ is the number of days expected for the PV system to work even when rain or clouds avoid the recharging of batteries usually is a design definition and has a value ranging from $0.5$ to $2$ days. $DOD$ is the depth of discharge or the fraction of discharge. The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries \textcolor{blue}{and represent an intrinsic and empirical feature of those type of batteries~\cite{Pinho} in order to guarantee its lifetime}; that represents a State of Charge ($SOC$) of $75$\% and $20$\% respectively, because $SOC=1-DOD$. However, it is worth separating the $DOD$ into two different definitions when the battery autonomy is larger than one day ($24$ hours). \textcolor{blue}{Therefore, the definition given here is for a maximum of $DOD$}. When we deal with daily $DOD$, we will call it $DOD_{day}$, and obviously, the sum of every $DOD_{day}$ can not exceed the maximum $DOD$.

In order to define the $DOD_{day}$, we use Eq.~\eqref{eq:DODday}. Moreover, the minimum current from the DC bus is defined by Eq.~\eqref{eq:Idcbus}. This equation is important to define the battery arrangement of the system (series and parallel connections). Where $V_{system}$ is the DC voltage of the bus.

\begin{subequations}
 \begin{tabularx}{\textwidth}{Xp{1cm}X}
\begin{equation}
\label{eq:DODday}
DOD_{day} = \dfrac{E_{corrected} \times 100}{E_{b}}
\end{equation}
 & &
\begin{equation}
\label{eq:Idcbus}
I_{min,DCbus} = \dfrac{E_{b}}{V_{system}}
\end{equation}
\end{tabularx}
\end{subequations}

As for batteries, we must first define the total capacity of the battery bank, which can be described as shown in Eq.~\ref{eq:Cbank}. where $ E_{load} $ is the average energy consumed by the load corrected according to PV equipment efficiency, and $ \eta_{b} $ is the efficiency of the battery.

\begin{equation}
\label{eq:Cbank}
\textcolor{blue}{C_{bank} = \dfrac{Autonomy \times E_{load}}{DOD \times \eta_{b} \times V_{system}}}
\end{equation}

Eq.~\ref{eq:batcheck} then performs the final sizing check, considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) adopted in the project.

\begin{equation}
\label{eq:batcheck}
\left( N_{BS} \times N_{BP} \right) \geq N_{B}total
\end{equation}

The charge controller must initially meet the voltage requirement of the PV system, as described by Eq.~\eqref{eq:vcvsystem}.

\begin{equation}
\label{eq:vcvsystem}
V_{c} = V_{system}
\end{equation}

\textcolor{blue}{The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq.~\eqref{eq:iscamb} for the ambient short-circuit current from the PV panel. $G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.}

\begin{equation}
\label{eq:iscamb}
I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right] 
\end{equation}

The controller must meet the maximum current from the PV array given by Eqs.~\eqref{eq:icmin} and~\eqref{eq:icicmin}. Where $N_{PP}$ is the number of parallel panels adopted.

\begin{subequations}
 \begin{tabularx}{\textwidth}{Xp{1cm}X}
\begin{equation}
\label{eq:icmin}
I_{c,min} = I_{sc,amb} \times N_{PP}
\end{equation}
& &
\begin{equation}
\label{eq:icicmin}
I_{c} \geq I_{c,min}
\end{equation}
\end{tabularx}
\end{subequations}

The number of controllers required for the off-grid PV system, as defined by \cite{Yatimi}, is calculated using Eq.~\eqref{eq:numberofcmin}. Besides, the final sizing check is performed by Eq.~\eqref{eq:numberofc}, which validates the number of controllers adopted.

\begin{equation}
\label{eq:numberofcmin}
number_{controllers} = \dfrac{Total \, max \, power \, of \, PV}{Controller \, max \, power} = \dfrac{P_{m,ref} \times N_{TP}}{V_{system} \times I_{controller,max}}
\end{equation}

\begin{equation}
\label{eq:numberofc}
N_{controller} \geq number_{controllers}
\end{equation}

The inverter sizing check is performed through three equations. Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load, i.e., the outlet voltage. Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage, and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.

\begin{subequations}
 \begin{tabularx}{\textwidth}{Xp{1cm}X}
\begin{equation}
\label{eq:vindc} 
V_{in}DC = V_{system}
\end{equation}
& &
\begin{equation}
\label{eq:voutac} 
V_{out}AC = V_{AC}
\end{equation}
\end{tabularx}
\end{subequations}

\begin{equation}
\label{eq:invcheck} 
\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right]
\end{equation}

Some inverter models allow parallel operation of more than one unit, besides the integration to create bi- and three-phase circuits. It is advisable to use pure sine wave inverters for electronic loads sensitive to harmonic distortion waves.

Besides that, it is crucial to verify the compatibility between the charge controller and inverter because some models are not compatible with equipment from other manufacturers. Furthermore, it is vital to select an inverter power that is lower than (or equal) the charge controller power, because the demand from the electric load causes the inverter to transfer this demand from the DC side. Then the controller can be overcharged during this operation and burn.

All the equations above model the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation. The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.

>>>>

The sizing check stage can ensure that the system meets the standard project steps related to the critical period method (worst month) for solar energy system sizing~\cite{Pinho} and adopting an MPPT (Maximum Power Point Tracking) charge controller, which is the most common in use.

\textcolor{blue}{In this paper, which audience is targeted to be from software verification area, we decided to use a higher level explanation about the PV sizing. The sizing process involve a set of 18 equations, related to electrical engineering area, which are detailed in <GoogleDrive here>. The flowchart pictured in Fig.~\ref{fig:flow}  is the overview of the steps that must be taken in order to size a stand-alone PV system}

\begin{figure}[h]
\fbox{\includegraphics[width=0.8\textwidth]{flowchart2}}
\centering
\caption{High level description of stand-alone PV system sizing process.}
\label{fig:flow} 
\end{figure}

\textcolor{blue}{On the left side of Fig.~\ref{fig:flow} it is possible to visualize the inputs need to size a PV system. There are requirements from the house to be electrified, there are design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}. Related to the equipment list, the designer can use few equipment or a vast one. It is possible, as well, do not adopt commercial equipment list. However, the result is a PV sizing of specific power/current/ or voltage values, and usually just close of real equipment that can be found in the market. That possibility has the drawback of possible incompatibility among equipment when the real one are bought and deployed.}

\textcolor{blue}{There are specific steps that aim the calculation of some variables and other related to the electrical compatibility validation among equipment items. Those represent different shades of gray of the  rectangle boxes. The start point usually is a candidate list of PV panels, change controller, battery, and inverter, as indicated at the top of Fig.~\ref{fig:flow}. The arrows, in the right side, it shows a point where some specific item is validated. The flowchart do not shows the returning point, but if the candidate item is not compatible with other, or do not meet some calculated requirement, it must be changed to other in order to follow the indicated flux. At the end of the flow, all the items are defined and the sizing is finished.}

\textcolor{blue}{All the 18 equations used, model} the continuous-time behaviour of the PV system; they produce real numbers except for the batteries and panels, where real numbers must be converted into integer ones, considering the minimum or maximum according to each equation. The verification and simulation tools need to handle non-linear real arithmetic to produce the correct result.
